\textbf{EECS 340: Assignment 3}

### 2020-02-21 assignment_3/article.tex
💄 Fix language and expressions.

However, we cannot determine the expicit relationship between  $A[2], A[3], B[1], B[2], C[1]$, thus we conduct another experiment and add the top two candidates to the result list. This step shall cost one experiment and thus carries a $T(1)$ runtime.

>>>>

However, we cannot determine the explicit relationship between  $A[2], A[3], B[1], B[2], C[1]$. Thus we conduct another experiment and add the top two candidates to the result list. This step shall cost one experiment and thus carries a $T(1)$ runtime.
